Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd
Add jpeg versions of images

```{r commonplace, fig.cap="Screenshots from the websites widenmypath.com (top) which includes top cycle route recommendations generated using the methods outlined in this paper in an open web forum, and salfordliveablestreets.commonplace.is (bottom) to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure.", fig.show='hold'}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics(c(
  "figures/widenmypath.png",
  "figures/saferstreets.png"
  ))
```

@@

```{r res, fig.cap="Results, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled."}
tmap_mode("view")
# tm_shape(r_pct_no_overlap) + tm_lines(col = "lightblue", lwd = 4, alpha = 0.6) +
#   tm_shape(r_pct_top) + tm_lines(col = "blue", lwd = 4, alpha = 0.6) +
#   tm_shape(r_pct_top_n) + tm_text("name") +
#   tm_shape(h_leeds) + tm_dots(size = 0.1)
knitr::include_graphics("figures/results-top-leeds.png") # this needs changing
```

>>>>

```{r commonplace, fig.cap="Screenshots from the websites widenmypath.com (top) which includes top cycle route recommendations generated using the methods outlined in this paper in an open web forum, and salfordliveablestreets.commonplace.is (bottom) to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure.", fig.show='hold'}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics(c(
  "figures/jpg/widenmypath.jpeg",
  "figures/jpg/saferstreets.jpeg"
  ))
```

@@

```{r res, fig.cap="Results of the Rapid Cycleway Prioritisation Tool, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled."}
tmap_mode("view")
# tm_shape(r_pct_no_overlap) + tm_lines(col = "lightblue", lwd = 4, alpha = 0.6) +
#   tm_shape(r_pct_top) + tm_lines(col = "blue", lwd = 4, alpha = 0.6) +
#   tm_shape(r_pct_top_n) + tm_text("name") +
#   tm_shape(h_leeds) + tm_dots(size = 0.1)
knitr::include_graphics("figures/results-top-leeds.png") # this needs changing
```
